\center \fontsize{18}{20} \selectfont Revealing the Landscape of Globally Color-Dual Multi-loop Integrands

### 2024-02-08 RefereeResponse/paper/2loopNLSM.tex
Alex's pass on reference for RefReport.

The kinematic numerators must be $D$-dimensional, Lorentz invariant,
local (polynomial) functions of the graph kinematics with the correct
power counting and external states. Locality is physically motivated since Feynman
rules produce polynomial numerators.
Indeed, the most natural way to guarantee locality and avoid spurious poles is to require the off-shell numerators to be polynomial functions of kinematics.
However, insisting on a local numerator is
partly a matter of convenience as the ansatz for a rational function
would quickly grow out of control without a guiding principle for what
terms to include.  %Referee edit
Historically, locality has also proved a highly successful tool for simplifying kinematic numerators. %Alex, can you add more relevant references to the next two sentences?
For example, the four-point function for $\mathcal{N}=4$ super-Yang Mills admits local color-dual numerators through four loops \cite{FivePointN4BCJ}.\footnote{At five loops, the most general local ansatz has not been explored, but the double copy has been performed at five loops using alternative methods \cite{FivePointN4BCJ}.}
While locality is well motivated from a physical and complexity
standpoint, the literature has featured numerators that violate
locality, modify naive power counting through the inclusion of higher
spin modes, and break manifest Lorentz invariance \cite{Square,
  WeinzierlBCJLagrangian, Mogull:2015adi, FivePointN4BCJ,
  Johansson:2017bfl, Ben-Shahar:2022ixa, Cheung:2016prv,
  Cheung:2021zvb}.  These developments suggest that relaxing locality
is a viable alternative when the condition proves too stringent for an
ansatz.  However, simply requiring on-shell locality may suffice.
This alternative will be discussed in \cref{nonLocalScattering}.

@@

\section{Two-loop four-point bootstrap}
\label{2loopBoot}
As we have just seen, it is possible to coerce tree numerators into
one-loop numerators at any multiplicity for pions and related
theories, but that these methods cannot be reapplied to generate
higher-loop numerators.  For pions in particular, the two-loop no-go statement
is only for \emph{one particular representation of the theory}, so it does
not completely preclude the existence of a two-loop color-dual
integrand.  We thus turn to the color-dual bootstrap method
described in \cref{sec:bootstrap} to construct a color-dual
representation of two-loop four-point NLSM.  Because of the similarity
of the problem setup, we will also use the opportunity to revisit the
construction of a color-dual representation of pure YM, extending the
search space beyond what was covered in Ref.~\cite{Bern:2015ooa} to include the most general local ansatz.
Even though this work is concerned with non-supersymmetric theories, recall that \ansatze{} techniques have been very successful for sYM.  %Referee edit
In particular, local color-dual representations have been found through 4pt 4-loop \cite{}. %What paper should we cite?
While a local representation has not been found at five loops, the double copy has still be performed \cite{FivePointN4BCJ}.

@@

Given the close ties between pion and gluon scattering for trees and
at one loop, the existence of the two-loop pion numerator prompts us
to investigate the most general local numerator for YM, without any of
the loop power counting assumptions of Ref.~\cite{Bern:2015ooa}.\footnote{As mentioned at the beginning of this section, \emph{supersymmetric} Yang-Mills is known to have a local color-dual representation at least through four loops \cite{BRY}.  A local but restricted ansatz fails at five loops, but the most general local ansatz has not been explored \cite{FivePointN4BCJ}.} %Referee edits.  What papers should we cite?
We follow the same general procedure as in \cref{sec:pions}, again
identifying the double-box and penta-triangle as the
Jacobi basis graphs and building the most general ansatz for each of
their numerators compatible with the assumptions in
\cref{sec:bootstrap}.  Because we are now considering pure
Yang-Mills, each monomial in the local ansatz must consist of five
Lorentz scalar dot products instead of the six for NLSM, and each
monomial must be linear in each of the four external gluon
polarizations.  Thus, the numerator ansatz for both diagrams will be
built from terms of the form
\begin{equation}
  N^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisDoubleBox} \right]
  \text{ and }
  N^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisPentaTriangle} \right]
  \in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
  \label{eq:ym-basis}
\end{equation}
where the $k_i$ take the same definition as described near
\cref{eq:scalar-basis}.  Without any power counting restrictions
imposed, both the double-box and the penta-triangle have an ansatz
with 10,010 terms each.  Imposing diagram automorphisms and
maximal-cut gauge invariance on the two basis diagrams, we reduce the
number of terms to 2,235 for the double-box, and 4,133 for the
penta-triangle.  The minimal set of spanning physical cuts is shown in
\cref{fig:ym-spanning}, but we choose to work within the framework of
the method of maximal cuts \cite{Bern:2007ct} in order to identify the
simplest cut that is in tension with the kinematic Jacobi relations.
Maximal cuts and symmetries are then imposed on the 14
non-pathological cubic diagrams shown above in \cref{fig:MaxCuts}.
Doing so, we are left with 596 total parameters in the ansatz.

>>>>

The kinematic numerators must be $D$-dimensional, Lorentz invariant,
local (polynomial) functions of the graph kinematics with the correct
power counting and external states. Locality is physically motivated
since Feynman rules produce polynomial numerators.  Indeed, the most
natural way to guarantee locality and avoid spurious poles is to
require the off-shell numerators to be polynomial functions of
kinematics.  However, insisting on a local numerator is partly a
matter of convenience as the ansatz for a rational function would
quickly grow out of control without a guiding principle for what terms
to include.  %Referee edit
Historically, locality has also proved a highly successful tool for
simplifying kinematic
numerators. %Alex, can you add more relevant references to the next two sentences?
For example, the four-point function for $\mathcal{N}=4$ super-Yang
Mills admits local color-dual numerators through four loops
\cite{Bern:2012uf}.\footnote{At five loops, the most general local
  ansatz has not been explored, but the double copy has been performed
  at five loops using alternative methods \cite{GeneralizedDoubleCopy,
    GeneralizedDoubleCopyFiveLoops}.}  While locality is
well motivated from a physical and complexity standpoint, the
literature has featured numerators that violate locality, modify naive
power counting through the inclusion of higher spin modes, and break
manifest Lorentz invariance \cite{Square, WeinzierlBCJLagrangian,
  Mogull:2015adi, FivePointN4BCJ, Johansson:2017bfl,
  Ben-Shahar:2022ixa, Cheung:2016prv, Cheung:2021zvb}.  These
developments suggest that relaxing locality is a viable alternative
when the condition proves too stringent for an ansatz.  However,
simply requiring on-shell locality may suffice.  This alternative will
be discussed in \cref{nonLocalScattering}.

@@

\section{Two-loop four-point bootstrap}
\label{2loopBoot}
As we have just seen, it is possible to coerce tree numerators into
one-loop numerators at any multiplicity for pions and related
theories, but that these methods cannot be reapplied to generate
higher-loop numerators.  For pions in particular, the two-loop no-go
statement is only for \emph{one particular representation of the
  theory}, so it does not completely preclude the existence of a
two-loop color-dual integrand.  We thus turn to the color-dual
bootstrap method described in \cref{sec:bootstrap} to construct a
color-dual representation of two-loop four-point NLSM.  Because of the
similarity of the problem setup, we will also use the opportunity to
revisit the construction of a color-dual representation of pure YM,
extending the search space beyond what was covered in
Ref.~\cite{Bern:2015ooa} to include the most general local ansatz.
Even though this work is concerned with non-supersymmetric theories,
recall that \ansatze{} techniques have been very successful for
sYM.  %Referee edit
In particular, local color-dual representations have been found
through 4pt 4-loop \cite{Bern:2012uf}. %What paper should we cite?
While a local representation has not been found at five loops, the
double copy has still be performed
\cite{GeneralizedDoubleCopy,GeneralizedDoubleCopyFiveLoops}.

@@

Given the close ties between pion and gluon scattering for trees and
at one loop, the existence of the two-loop pion numerator prompts us
to investigate the most general local numerator for YM, without any of
the loop power counting assumptions of
Ref.~\cite{Bern:2015ooa}.\footnote{As mentioned at the beginning of
  this section, \emph{maximally supersymmetric} Yang-Mills is known to have a
  local color-dual representation at least through four loops
  \cite{Bern:2012uf}.  A local but restricted ansatz fails at five loops, but
  the most general local ansatz has not been explored
  \cite{GeneralizedDoubleCopyFiveLoops}.} %Referee edits.  What papers should we cite?
We follow the same general procedure as in \cref{sec:pions}, again
identifying the double-box and penta-triangle as the Jacobi basis
graphs and building the most general ansatz for each of their
numerators compatible with the assumptions in \cref{sec:bootstrap}.
Because we are now considering pure Yang-Mills, each monomial in the
local ansatz must consist of five Lorentz scalar dot products instead
of the six for NLSM, and each monomial must be linear in each of the
four external gluon polarizations.  Thus, the numerator ansatz for
both diagrams will be built from terms of the form
\begin{equation}
  N^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisDoubleBox} \right]
  \text{ and }
  N^{\text{YM}}\left[\scalebox{0.75}{\NLSMBasisPentaTriangle} \right]
  \in \text{span}\left\{(\varepsilon_i \varepsilon_j) , (k_i \varepsilon_j), (k_ik_j)\right\}
  \label{eq:ym-basis}
\end{equation}
where the $k_i$ take the same definition as described near
\cref{eq:scalar-basis}.  Without any power counting restrictions
imposed, both the double-box and the penta-triangle have an ansatz
with 10,010 terms each.  Imposing diagram automorphisms and
maximal-cut gauge invariance on the two basis diagrams, we reduce the
number of terms to 2,235 for the double-box, and 4,133 for the
penta-triangle.  The minimal set of spanning physical cuts is shown in
\cref{fig:ym-spanning}, but we choose to work within the framework of
the method of maximal cuts \cite{Bern:2007ct} in order to identify the
simplest cut that is in tension with the kinematic Jacobi relations.
Maximal cuts and symmetries are then imposed on the 14
non-pathological cubic diagrams shown above in \cref{fig:MaxCuts}.
Doing so, we are left with 596 total parameters in the ansatz.
